---
title: "Lab 0 - Hello R!"
author: "[KAITLYN MAHER]"
date: "[JANUARY 17, 2022]"
format: pdf
editor: visual
---

## Load Packages

```{r}
#| label: load-packages
#| message: false

library(tidyverse)
library(datasauRus)
```

## Exercise 1

The datasaurus_dozen file has 1846 rows and 3 variables: 1) the dataset, 2) x-values, and 3) y-values.

## Exercise 2

(The answer for this exercise is given below, but you should clean up the narrative so it only includes what you want to turn in.)

First, let's plot the data in the dino dataset (we will cover **ggplot2** in much more depth next week):

```{r}
#| label: plot-dino
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) + 
  geom_point()
dino_data |>
  summarize(r = cor(x, y))
```

Next calculate the correlation between `x` and `y` in this dataset.

```{r}
#| label: cor-dino
dino_data %>%
  summarize(r = cor(x, y))
```

## Exercise 3

(Add code and narrative here as needed. Note the code chunks below are labeled with `plot-circle` and `cor-circle` to provide spaces to place the code for plotting and calculating the correlation coefficient.)

(When you have finished, delete these instructions.)

```{r}
#| label: plot-circle
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) + 
  geom_point()
circle_data |>
  summarize(r = cor(x, y))
```

Some more narrative can go here.

```{r}
#| label: cor-circle
circle_data %>%
  summarize(r = cor(x, y))
```

Conclude with some more narrative, if needed.

## Exercise 4

(Add a labeled code chunk and narrative here. Insert code chunks using the "insert chunk" button (a green C with a +). Alternatively, use CMD + OPTION + I (Mac) or CTRL + ALT + I (Windows).)

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
datasaurus_dozen |>
  group_by(dataset) |>
  summarize(r = cor(x, y)) 
```

## Exercise 5

(Add a labeled code chunk and narrative here. Insert code chunks using the "insert chunk" button (a green C with a +). Alternatively, use CMD + OPTION + I (Mac) or CTRL + ALT + I (Windows).)
